### 2012-12-14 doc/description.tex
owningClass function

\begin{itemize}
	\item Class : Class represents a basic structural concept in the application model. It has a unique name, one or more properties and a class can be associated to other classes in the application.

$$Class = (label, Property*, Association*)$$
$name : Class \rightarrow Label$ \\
$name((lab, props, assocs)) = lab$ \\ \\
$properties : Class \rightarrow Property*$ \\
$properties((lab, props, assocs)) = props $\\ \\
$primitiveProperties : Class \rightarrow Property*$ \\
$primitiveProperties((lab, props, assocs)) = props \wedge \forall p \in props : cardinality(p) \leq 1 $\\ \\
$collectionProperties : Class \rightarrow Property*$ \\
$collectionProperties((lab, props, assocs)) = props \wedge \forall p \in props : cardinality(p) > 1 $\\ \\
$associations : Class \rightarrow Association*$ \\
$associations((lab, props, assocs)) = assocs $

	\item Property : Property represents a feature of  a class which is can be represented as a primitive type. The property can be mandatory, can have a default value.
$$
Property = (label, AppType, DefaultValue, Cardinality)
$$
$name : Property \rightarrow Label$ \\
$name((lab, t, val, n)) = lab$ \\ \\
$type : Property \times AppType$ \\
$type((lab, t, val, n)) = t$ \\ \\
$cardinality : Property \rightarrow NzNat$ \\
$cardinality((lab, t, val, n)) = n$

%TODO owning class
	\item Association : the association represents a connection between two classes. It has a unique name and it contains a name of the class which is referenced by the association. The class which owns the association is consider to be a starting class of an association, referenced class is consider to be an ending class of an association. The cardinalities defines the multiplicity of the association.
$$
Association = (label, classRef, startCardinality, endCardinality)
$$
$name : Association \rightarrow Label$ \\
$name((lab, ref, n_1, n_2)) = lab$\\ \\
$reference : Association \rightarrow Label$ \\
$reference((lab, ref, n_1, n_2)) = ref$\\ \\
$startCardinality : Association \rightarrow NzNat$ \\
$startCardinality((lab, ref, n_1, n_2)) = n_1$\\ \\
$endCardinality : Association \rightarrow NzNat$ \\
$endCardinality((lab, ref, n_1, n_2)) = n_2$

	\item App-Type : represents primitive types in the application. There are usually defined types such as String, Integer, Boolean etc. in contrast there is only one type in our model, because we focus on structural and data changes and type casting operations are not important for us. The only App-Type type is called APP-STRING.
$$
AppType = APPSTRING
$$
\end{itemize}
The types used in application model:
$$
cardinality = NzNat
$$
$$
referencesClass = label
$$
$$
startCardinality = NzNat
$$
$$
endCardinality = NzNat
$$
$$
NzNat = [0 - 9]*
$$

>>>>

\paragraph{Class} represents a basic structural concept in the application model. It has a unique name, one or more properties and a class can be associated to other classes in the application.

$$Class = (label, Property*, Association*)$$
$name : Class \rightarrow Label$ \\
$name((lab, props, assocs)) = lab$ \\ \\
$properties : Class \rightarrow Property*$ \\
$properties((lab, props, assocs)) = props $\\ \\
$primitiveProperties : Class \rightarrow Property*$ \\
$primitiveProperties((lab, props, assocs)) = props', \forall p \in props' : cardinality(p) \leq 1 $\\ \\
$collectionProperties : Class \rightarrow Property*$ \\
$collectionProperties((lab, props, assocs)) = props', \forall p \in props' : cardinality(p) > 1 $\\ \\
$associations : Class \rightarrow Association*$ \\
$associations((lab, props, assocs)) = assocs $

\paragraph{Property} represents a feature of  a class which is can be represented as a primitive type. The property can be mandatory, can have a default value.
$$
Property = (label, AppType, DefaultValue, Cardinality)
$$
$name : Property \rightarrow Label$ \\
$name((lab, t, val, n)) = lab$ \\ \\
$type : Property \times AppType$ \\
$type((lab, t, val, n)) = t$ \\ \\
$cardinality : Property \rightarrow NzNat$ \\
$cardinality((lab, t, val, n)) = n$ \\ \\
$owningClass : Property \times Application \rightarrow Class $ \\
$owningClass(p, a) = c, c \in classes(a) \wedge p \in properties(c) $

\paragraph {Association} represents a connection between two classes. It has a unique name and it contains a name of the class which is referenced by the association. The class which owns the association is consider to be a starting class of an association, referenced class is consider to be an ending class of an association. The cardinalities defines the multiplicity of the association.
$$
Association = (label, classRef, startCardinality, endCardinality)
$$
$name : Association \rightarrow Label$ \\
$name((lab, ref, n_1, n_2)) = lab$\\ \\
$reference : Association \rightarrow Label$ \\
$reference((lab, ref, n_1, n_2)) = ref$\\ \\
$startCardinality : Association \rightarrow NzNat$ \\
$startCardinality((lab, ref, n_1, n_2)) = n_1$\\ \\
$endCardinality : Association \rightarrow NzNat$ \\
$endCardinality((lab, ref, n_1, n_2)) = n_2$ \\ \\
$owningClass : Association \times Application \rightarrow Class $ \\
$owningClass(as, a) = c, c \in classes(a) \wedge as \in associations(c) $

\paragraph{AppType} represents primitive types in the application. There are usually defined types such as String, Integer, Boolean etc. in contrast there is only one type in our model, because we focus on structural and data changes and type casting operations are not important for us. The only App-Type type is called APP-STRING.
$$
AppType = APPSTRING
$$
The types used in application model:
$$
cardinality = NzNat
$$
$$
referencesClass = label
$$
$$
startCardinality = NzNat
$$
$$
endCardinality = NzNat
$$
$$
NzNat = [0 - 9]*
$$
